Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2017-12-29 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Correction

The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}. However, due to relatively low mesh resolution, in particular above and below the central channel region, capture of fingers (formation and growth) was very limited. A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from XX to XX tetrahedral \PNDG[1]{1} element-pairs. Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.

>>>>

The progress of the saturation front and formation and growth of fingers in time and space can be seen in more details in isosurfaces shown in Fig.~\ref{fig:3DChannel_Isosurf}. A numerical simulation of the same problem (\ie same geometry, initial mesh, initial and boundary conditions) was also performed using an adaptive mesh, Fig.~\ref{fig:3DChannel_sat_adapt}, with resolution ranging from 235242 to 643064 tetrahedral \PNDG[1]{1} element-pairs. Distinct preferable flow pathways are shown  For the same time-steps an inner view on the domain provides with a more detailed description of not only the flow path itself as well as the minor fingers that may be created. At this point resolution plays an important role on capturing these patterns in detail and is also a limititation that needs to be overcome.
